Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-14 paper/paper.tex
pass on text

\subsection{Suricata Rules}

@@

\tname{} is a search-based algorithm that uses positive and negative
examples to synthesize signature-based rules, such as those from Snort
and Suricata. \tname{} synthesizes rules in two steps. First, it
produces an overspecified rule to capture the negative example
provided as input. Then, it uses positive examples to eliminate
unecessary options from the rule. The goal is to create a rule that
captures only the negative traffic.

@@

@@

>>>>

\subsection{Suricata Rules}
\label{sec:example-suricata-rules}

@@

\tname{} is a search-based algorithm that uses positive and negative
examples to synthesize signature-based NIDS rules, such as those from
Snort and Suricata. \tname{} synthesizes rules in two steps. First, it
produces a potentially overspecified rule that captures the negative
example provided as input. Then, it uses positive examples to
eliminate unecessary options from the rule. The goal is to create a
rule that captures only the negative traffic.

@@

\tname{} uses an abstract representations of a Suricata rule that
reflects the concrete representation of the rule. The concrete rule
representation is the one actually used by Suricata whereas the
abstract representation is the one \tname{} uses to run the
search. The abstract representation encodes the rule options segment
(see Section~\ref{sec:example-suricata-rules}) of a Suricata rule as a
vector of Option objects. For example, \tname{} models the option
\CodeIn{flags} from the example on Figure~\ref{fig:synflood-example},
with a data structure storing two fields, one of character type and
another of integer type. This enables \tname{} to mutate each element
separately.\Mar{Lucas, por favor, confirme.}

@@

\tname{} is a single-individual hill-climbing like search.
